An Empirical Analysis of the Internet Engineering Task Force with Computational Methods

### 2024-10-06 paper.tex
Expand discussion of drafts in §5.1

%..................................................................................................
\pb{Discussion of draft documents:}
The mailing lists are, other than plenary or interim meetings, the primary
means for the discussion of draft documents. To measure how often drafts are
discussed, we identify mentions of Internet-Drafts and RFCs in mailing list
messages.  We extract any mention of a draft (beginning \texttt{draft-}) or
RFC (i.e., ``RFC'' followed by a number).  Figure~\ref{fig:draft_mentions}
presents the number of drafts mentions in the emails per year. Separate
mentions of the same draft are counted as different mentions, as we want to
observe the entire volume of mentions.  We observe a strong increase in the
number of mentions over time.  This is largely driven by the growing number
of drafts being published. In fact, we find a Pearson correlation of 0.89
between the number of drafts published and the number of mentions. This
speaks to the influence of emails that mention drafts in driving draft
production.
\todo{Add and cross-reference a discussion of number of drafts published
over time in Section \ref{sec:trends-documents}. Does this tie into the
discussion of increasing complexity of draft publication?}

>>>>

%..................................................................................................
\pb{Discussion of draft documents:}
The mailing lists are, other than plenary or interim meetings, the primary
means for the discussion of draft documents. To measure how often drafts are
discussed, we identify mentions of Internet-Drafts and RFCs in mailing list
messages.  We extract any mention of a draft (beginning \texttt{draft-}) or
RFC (i.e., ``RFC'' followed by a number).  Figure~\ref{fig:draft_mentions}
presents the number of drafts mentions in the emails per year. Separate
mentions of the same draft are counted as different mentions, as we want to
observe the entire volume of mentions.  We observe a strong increase in the
number of mentions over time.

% This is largely driven by the growing number of drafts being published. In
% fact, we find a Pearson correlation of 0.89 between the number of drafts
% published and the number of mentions. This speaks to the influence of
% emails that mention drafts in driving draft production.

When compared with the number of active drafts (Figure \ref{fig:drafts-by-date}
in \S\ref{sec:trends-documents:production}) we see that the number of mentions
of work-in-progress drafts and RFCs is increasing faster than the number of
such documents. This further supports the hypothesis of increasing standards
complexity---discussion is increasingly referencing prior standards and
other work in progress, as would be expected if the task of ensuring
compatibility with that work is growing in complexity.
